### 2009-02-24 doc/ws-programming-tutorial/doc/tex_pesistentservice/peristentservice.tex
Small modifications...

if bartender_url.startswith('https'):
    key_file = os.environ.get('ARC_KEY_FILE', None)
    cert_file = os.environ.get('ARC_CERT_FILE', None)
    proxy_file = os.environ.get('ARC_PROXY_FILE', None)
    ca_file = os.environ.get('ARC_CA_FILE', None)
    ca_dir = os.environ.get('ARC_CA_DIR', None)

export ARC_KEY_FILE=/local/glodek/clientKey.pem
export ARC_CA_FILE=/local/glodek/clientCA.pem
export ARC_CERT_FILE=/local/glodek/clientCert.pem

>>>>

    key\_file = os.environ.get('ARC\_KEY\_FILE', None)
    cert\_file = os.environ.get('ARC\_CERT\_FILE', None)
    proxy\_file = os.environ.get('ARC\_PROXY\_FILE', None)
    ca\_file = os.environ.get('ARC\_CA\_FILE', None)
    ca\_dir = os.environ.get('ARC\_CA\_DIR', None)

export ARC\_KEY\_FILE=/local/glodek/clientKey.pem
export ARC\_CA\_FILE=/local/glodek/clientCA.pem
export ARC\_CERT\_FILE=/local/glodek/clientCert.pem
